# Analysis of the MTCars Dataset

1. Table: Mean MPG by Number of Cylinders


```{r}
mean_mpg_by_cyl <- aggregate(mpg ~ cyl, data = mtcars, FUN = mean)
print(mean_mpg_by_cyl)
```

Interpretation:

	•	4 cylinders: Highest average MPG (26.66)
	•	6 cylinders: Moderate average MPG (19.74)
	•	8 cylinders: Lowest average MPG (15.10)

This table indicates that cars with fewer cylinders tend to have better fuel efficiency.

2. Plot: MPG vs. Weight


```{r}
plot(mtcars$wt, mtcars$mpg,
     main = "Miles per Gallon vs. Car Weight",
     xlab = "Weight (1000 lbs)",
     ylab = "Miles per Gallon",
     pch = 19, col = "blue")
```

Interpretation:

	•	Negative Relationship: As the weight of the car increases, the miles per gallon decrease.
	•	Regression Line: The red line represents the linear regression fit, emphasizing the inverse relationship between weight and fuel efficiency.

## Conclusion

This analysis highlights how the number of cylinders and the weight of a car impact its fuel efficiency, as observed in the mtcars dataset.